FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-08-19 paper.tex
png → pdf

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/genpropkill-outline.png}
  \caption{Gen, Prop, Kill: Lifetime of an exceptional value}
  \label{f:gpk}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{./fig/cstg_static_diagram.png}
  \caption{From stack traces (left) to \CSTG{} (right)}
  \label{fig:cstg_demo}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=3in]{./fig/shallow_waters_cfl_diff.png}
  \caption{Raising the CFL number creates white gaps due to \NaN{}s}
  \label{fig:sw_nans}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.96\columnwidth]{fig/sw_nan_cstg_clean.png}
  \caption{Stack graph for \NaN{} gens in shallow waters}
  \label{fig:sw_nan_cstg}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.96\columnwidth]{./fig/cstg_diff_pretty.png}
  \caption{Stack graph diff}
  \label{fig:cstg_diff_demo}
\end{figure}

>>>>

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/genpropkill-outline.pdf}
  \caption{Gen, Prop, Kill: Lifetime of an exceptional value}
  \label{f:gpk}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{./fig/cstg_static_diagram.pdf}
  \caption{From stack traces (left) to \CSTG{} (right)}
  \label{fig:cstg_demo}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=3in]{./fig/shallow_waters_cfl_diff.pdf}
  \caption{Raising the CFL number creates white gaps due to \NaN{}s}
  \label{fig:sw_nans}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.96\columnwidth]{fig/sw_nan_cstg_clean.pdf}
  \caption{Stack graph for \NaN{} gens in shallow waters}
  \label{fig:sw_nan_cstg}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.96\columnwidth]{./fig/cstg_diff_pretty.pdf}
  \caption{Stack graph diff}
  \label{fig:cstg_diff_demo}
\end{figure}
